JLyrics

### 2014-08-03 report/paper.tex
Added Unicode citations. Removed Discussion section.

\subsection{Platform Dependent Results}

@@

In order to understand the problem with mojibake, a discussion of character encodings will need to be presented. A single character such as the letter ``a'' must be represented in a format that a computer can understand. At its absolute lowest level, a computer can only store data in the form of ones and zeros. The number system that contains only these two numbers is called binary. However, the string of bits we choose to encode a particular character in is completely arbitrary. To that extent, the ASCII (American Standard Code for Information Interchange) format was invented so that everyone programming on computers would follow the same format for encoding a set of characters. For example, ``a'' is represented in ASCII format as ``0110 0001''. ASCII was invented in the very young days of computing, so there was no intention of supporting alphabets and character sets beyond what Latin characters could represent (for example, English).

@@

As time went on, a new standard of expressing characters as strings of bytes appeared called Unicode. It proposed blueprints of how one should represent characters form any and all alphabets in a set length of bits. Unicode is an abstract concept \cite{unicode-abstract}. The most popular encoding of Unicode to this day is UTF-8 (Unicode Transformation Format 8). Many Japanese developers are content with Shift-JIS even though the Shift-JIS encoding can't handle non-Japanese and non-Latin characters, so there is a struggle involved with dealing with Japanese text such that one must check if the text was encoded in Shift-JIS, UTF-8, or something else.

@@

\section{Discussion}

Are there any interesting questions or findings that should be discussed?

>>>>

\pagebreak
\subsection{Platform Dependent Results}

@@

In order to understand the problem with mojibake, a discussion of character encodings will need to be presented. A single character such as the letter ``a'' must be represented in a format that a computer can understand. At its absolute lowest level, a computer can only store data in the form of ones and zeros. The number system that contains only these two numbers is called binary. However, the string of bits we choose to encode a particular character in is completely arbitrary. To that extent, the ASCII (American Standard Code for Information Interchange) format was invented so that everyone programming on computers would follow the same format for encoding a set of characters \cite[p.~1]{ascii}. For example, ``a'' is represented in ASCII format as ``0110 0001''. ASCII was invented in the very young days of computing, so there was no intention of supporting alphabets and character sets beyond what Latin characters could represent (for example, English).

@@

After the advent of Shift-JIS, a new standard of expressing characters as strings of bytes appeared called Unicode \cite{sjis}. It proposed blueprints of how one should represent characters form any and all alphabets in a set length of bits. Unicode is an abstract concept \cite{unicode-abstract}. The most popular encoding of Unicode to this day is UTF-8 (Unicode Transformation Format 8). Many Japanese developers are content with Shift-JIS even though the Shift-JIS encoding can't handle non-Japanese and non-Latin characters, so there is a struggle involved with dealing with Japanese text such that one must check if the text was encoded in Shift-JIS, UTF-8, or something else.

@@
